---
title: "AMS380 - Homework 02"
author: 'Tuan Bui, SBU ID: 113141951'
date: "9/9/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1:

Generate 100 random samples following Poission distribution with lambda = 5.

```{r}
rpois(100, lambda = 5)
```

Histogram of the sample

```{r}
hist(rpois(100, lambda = 5))
```

Question 2

a. 6 < X < 8 if X follows an exponential distribution with rate is 3

```{r}
pexp(8, rate =3) - pexp(6, rate = 3)
```
  Answer: The probability of 6 < X < 8 if X follows an exponential distribution with rate is 3: 1.519223e-08

b. X > 10 if X follows a normal distribution with mean is 8 and standard is 3

```{r}
pnorm(10, mean = 8, sd = 3, lower.tail = F)
```
  Answer: The probability of X > 10 if X follows a normal distribution with mean is 8 and standard is 3: 0.2524925

c. X^2 < 5 if X follows a binomial distribution with size 20 and prob is 0.4

```{r}
pbinom(sqrt(5), size = 20, prob = 0.4)
```
  Answer: The probability of X^2 < 5 if X follows a binomial distribution with size 20 and prob is 0.4

Question 3
```{r}
combination_base <- choose(300, 110)^2
prop <- 0
sq <- 55
dq <-55
#probability of 2 students getting at least 50% of the test

repeat{
  prop <- ((choose(300,110)*choose(110,sq)*choose(190,dq))/combination_base) + prop
  sq <-sq + 1
  dq <- dq -1
  if(sq == 110) break
}
prop
```
  The probability that 2 students get at least the same 50% of the test is 0.0002275255

Question 4

```{r}
# H0: mu_man = mu_woman Ha: mu_man != mu_woman
# load data
woman <- c(38.9, 61.2, 73.3, 21.8, 63.4, 64.6, 48.4, 48.8, 48.5)
man <- c(67.8, 60.0, 63.4, 76.0, 89.4, 73.3, 67.3, 61.3, 62.4)

# visualize data by box plot
boxplot(woman, man, names = c('woman', 'man'))

shapiro.test(woman)
shapiro.test(man)

# p-value of the shapiro-test of both samples are 0.6101 and 0.1066, which are greater than the significance level(0.05), not reject H0, both samples are normal.

var.test(woman,man)
var.test(man,woman)

# p-value of the variance test is 0.1714, which is greater than the significance level (0.05), not reject H0, the variance of both samples are assumed to be the same.

t.test(woman, man, mu = 0, var.equal = T)

# p-value of the t-test is 0.01327, which is less than the significance level 0.05, reject H0, the mean of woman'weight and man's weight are significantly different.
```

Question 5

```{r}
#H0: mu_before = mu_after, Ha: mu_before <= mu_after
# load data
before <- c(200.1, 190.9, 192.7, 213.0, 241.4, 196.9, 172.2, 185.5, 205.2, 193.7)
after <- c(392.9, 393.2, 345.1, 393.0, 434.0, 427.9, 422.0, 383.9, 392.3, 352.2)
diff <- after - before

# visualize data by box plot
boxplot(before, after, names = c('before', 'after'))

shapiro.test(diff)

# p-value of shapiro test of the different is 0.6141, greater than the significance level 0.05, not reject H0, the different can be assumed normal.

t.test(diff, mu = 0, alternative = 'greater', conf.level = 0.9)

# p-value of the paired sample t-test is less than the significance level 0.10, reject H0, the mean of the weight after is significantly greater than one before.
```

