---
title: "AMS 315 - Project 01"
author: "TUAN BUI"
date: "10/16/2021"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part A

```{r}
library(mice)
library(knitr)

wdir <- "~/OneDrive - Stony Brook University/SBU/MAT + AMS/Fall 2021/AMS 315/project/01/Data"
setwd(wdir)

PartA_IV <- read.csv("141951_IV.csv", header = T)
PartA_DV <- read.csv("141951_DV.csv", header = T)
PartB <- read.csv("141951_PartB.csv", header = T)

PartA <- merge(PartA_IV, PartA_DV, by = 'ID')

str(PartA_IV)
min(PartA_IV$ID)
str(PartA_DV)
str(PartA)
```

[Report:]{.ul}

> There are 540 observations in this file and three columns in the data set, called 'ID', 'IV' and 'DV'. Each is numerical.

```{r}
md.pattern(PartA)
```

[Report:]{.ul}

> There are 451 complete data sets.
>
> IV is missing in 47 cases, DV is missing in 58 cases, and both IV and DV are missing in 16 cases.

```{r}
PartA_imp <- PartA[!is.na(PartA$IV)==TRUE|!is.na(PartA$DV)==TRUE,]
imp <- mice(PartA_imp, method = "norm.boot", printFlag = FALSE)
PartA_complete <- complete(imp)

md.pattern(PartA_complete)
```

[Report:]{.ul}

> There are 524 complete data sets after imputing missing data. There are no data for 16 observations

```{r}
fit <- lm(DV ~ IV, data = PartA_complete)
summary(fit)
```

```{r}
kable(anova(fit), caption='ANOVA Table')
```

```{r}
plot(PartA_complete$DV ~ PartA_complete$IV, main='Scatter : DV ~ IV', xlab= "IV", ylab = "DV")
abline(fit, col='red', lty=3, lwd=2)
legend('topleft', legend='Estimated Regression Line', lty=3, lwd=2, col='red')
```

95% confidence interval of the slope:

```{r}
confint(fit, level = 0.95)
```

99% confidence interval of the slope

```{r}
confint(fit, level = 0.99)
```

# Part B

```{r}
fit_trial <- lm(sqrt(PartB$y) ~ PartB$x)
plot(sqrt(PartB$y) ~ PartB$x)
abline(fit_trial)

summary(fit_trial)

PartB_trans <- data.frame(xtrans = PartB$x, ytrans = sqrt(PartB$y))

cor(PartB_trans$xtrans, PartB_trans$ytrans)

confint(fit_trial, level = 0.95)

confint(fit_trial, level = 0.99)

groups <- cut(PartB_trans$xtrans, breaks = c(-Inf, seq(min(PartB_trans$xtrans) + 0.3, max(PartB_trans$xtrans) - 0.3, by = 0.3), Inf))
table(groups)

x_b <- ave(PartB_trans$xtrans, groups)
data_bin <- data.frame(x = x_b, y = PartB_trans$ytrans)

library(remotes)
library(alr3)

fit_b <- lm(y ~ x, data = data_bin)
pureErrorAnova(fit_b)
```
